Reionization Planck 2018 Notes

### 2020-07-09 results/notes.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_vs_mock_gaussian_fp10_fp14.png
}
\caption{NEW - comparing f = 0.10 and 0.14 in python KDE (latest version) against an example of gaussian smoothing with 0.10, 0.14 on a symmetric Gaussian function.
}
\label{fig:}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_vs_mock_gaussian_fp10_fp14.png}
\caption{NEW - comparing f = 0.10 (orange dotted) and 0.14 (green dotted) in python KDE (latest version) against an example of gaussian smoothing with f = 0.10 (orange dashed) and 0.14 (blue dashed) on a Gaussian function (blue solid).
}
\label{fig:}
\end{figure}
